\huge A Usability Evaluation of Tor Launcher

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Remove double "and" in a sentence.

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

>>>>

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
